Building Large-Scale Cross-lingual Knowledge Base from Multi-Encyclopedia

### 2015-06-06 nlpcc/paper.tex
老大的修改

\usepackage{xeCJK}
\setCJKmainfont[BoldFont=STHeiti, ItalicFont=STKaiti]{STSong}
\setCJKsansfont[BoldFont=STHeiti]
\setCJKmonofont{STFangsong}

%\usepackage[BoldFont,SlantFont,CJKchecksingle]{xeCJK}
%\setCJKmainfont[BoldFont=SimHei]{SimSun}
%\setCJKmonofont{SimSun}% 设置缺省中文字体
%\usepackage{CJKutf8}

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
%\usepackage{CJK}

\usepackage{url}
\usepackage[ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{multirow}

\urldef{\mailthu}\path|{lmy13@}tsinghua.edu.cn|
\urldef{\mailsy}\path|{fantasysy@}sina.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
\newcommand{\para}[1]{\vspace{0.1cm}\noindent\textbf{#1}}

\begin{document}
%\begin{CJK*}{UTF8}{simsun}
\mainmatter

@@

\section{Introduction}
With Linked Open Data(LOD) developing recent years, an increasing number of knowledge bases are generated for information sharing. Large-scale knowledge bases in LOD project, such as DBpedia\cite{mendes2012dbpedia}, YAGO\cite{mahdisoltani2014yago3} and Freebase\cite{bollacker2008freebase} are often used for information extraction\cite{dutta2013integrating}, entity linking\cite{shen2012linden}, recommendation\cite{passant2010dbrec,fernandez2011generic,kaminskas2012knowledge} and many other applications. These knowledge bases are not only cross-domain but also multilingual, which is benefit for global knowledge sharing.

DBpedia, the nucleus of LOD, extracts structured information from Wikipedia and contains approximately 38.3 million things. Now DBpedia provides 124 versions of non-English language including Chinese. However, there are only XXX instances and 11 classes in Chinese. Compared with the 4.58 million things in English, the quantity of Chinese information is obviously insufficient for further research and application.

A cross-lingual knowledge base can effectively promote global knowledge sharing, understanding and expanding. However, to build an practical knowledge base, some problems must be addressed: (1) The imbalance of different language source size leads to less entities. Comparing the number of articles in English Wikipedia with those in Chinese Wikipedia, which are 5 million and 800 thousand separately, it's obvious that to structure a knowledge base in Chinese with Wikipedia is more challenging. (2) The low proportion of existing cross-lingual links in Wikipedia affects the quality of a bilingual knowledge base. Statistically, only XX\% articles have cross-lingual links between English and Chinese in all articles of the two languages. Especially scarce evident links for infobox attribute. (3) The large but not rigorous category system in Wikipedia causes incorrect semantic relations in taxonomy. For example,\textcolor{red}{example}

%In Semantic Web, a large-scale multilingual knowledge base can help …

%Thus it’s significant to build a Chinese-English knowledge base and benefit from it.

Currently, there are several massive knowledge encyclopedias in Chinese, including Hudong Baike and Baidu Baike. To solve the imbalance problem, we utilize such monolingual sources to enrich our Chinese information. In this paper, we propose a pipeline to integrate four resources, English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike, into one cross-lingual knowledge base, which contains XXX classes, XXX instances and XXX properties. During the whole procedure, we also expand language links and make judgement on the semantic relations. Based on the obtained result, we develop an online website, which supports keyword search and SPARQL endpoint to our knowledge base. Specifically, our work makes the following contributions:
\begin{itemize}
  \item We propose a method to build a Chinese-English cross-lingual knowledge base combining multi-encyclopedia. Among them, Chinese encyclopedias are utilized to help balance and enrich information in two languages.
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{itemize}

The rest of the paper is organized as follows. Section \ref{sec:pd} introduces the related classes and defines the problem of building a cross-lingual knowledge base. Section \ref{sec:dp} presents the extraction approaches in class, instance and property level. Section \ref{sec:clkbb} describes the procedure of building a knowledge base using extracted result. Section \ref{sec:result} demonstrates the data situation of established knowledge base. Section \ref{sec:work} reviews the related literatures. Section \ref{sec:con} concludes this paper and points out some future directions of this work.

@@

\subsection{Web Access to Knowledge Base}
We provide a website to present an intuitive graph of our knowledge in the forms of class, instance and property. Fig.\ref{fig:xlore} shows sample pages of the integrated data. Users can choose language preference which is convenient for both English speaker and Chinese speaker. In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.  In the instance webpage we display bilingual label, super classes, related classes, abstract, property key value pairs, images and references. In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/xlore}}
    \caption{Sample Pages of Class, Instance and Property}
    \label{fig:xlore}
\end{figure}%
Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}. For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label. To present practicable result, An index is generated over all entities. We as well provide SPARQL interface for professional users to query our knowledge graph. Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}. For example, to get the English label of an instance, the query is: select * where {<http://xlore.org/instance/100> <http://www.w3.org/2000/01/rdf-schema#label> ?label. filter(langMatches(?label),"en"))}.

@@

%\end{CJK*}
\end{document}

>>>>

\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{CJK}
\usepackage{url}
\usepackage[ruled]{algorithm2e}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{multirow}

\urldef{\mailthu}\path|{lmy13}@tsinghua.edu.cn|
\urldef{\mailsy}\path|{fantasysy}@sina.com|
\newcommand{\keywords}[1]{\par\addvspace\baselineskip\noindent\keywordname\enspace\ignorespaces#1}
\newcommand{\para}[1]{\vspace{0.1cm}\noindent\textbf{#1}}

\begin{document}
\begin{CJK*}{UTF8}{song}
\mainmatter

@@

\section{Introduction}

As the Web is evolving to a highly globalized information space, sharing knowledge across different languages is attracting increasing attentions. Multilingual knowledge bases have significant applications such as multi-lingual information retrieval, machine translation and deep question answering. DBpedia, by extracting structured information from Wikipedia\footnote{{\tt http://www.wikipedia.org/}} in XXX different languages, is a multi-lingual multi-domain knowledge base and becomes the nucleus of LOD\footnote{{\tt http://linkeddata.org/}}. Obtained from the automatic integration of WordNet\footnote{{\tt http://wordnet.princeton.edu/}} and Wikipedia, YAGO, MENTA and BabelNet are other famous large multi-lingual knowledge bases.

However, most non-English knowledge in those knowledge bases is pretty scarce. Figure \ref{fig_stat} shows a simplified long tail distribution of the number of articles on six major Wikipedia language versions. Due to the imbalance of different Wikipedia language versions, the knowledge distribution across different languages is highly unbalanced in those knowledge bases which are generated from Wikipedia. For instance, DBpedia contains XXX English instances but only XXX Chinese instances. On the other hand, the Chinese Hudong Baike\footnote{{\tt http://www.baike.com/}} and Baidu Baike\footnote{{\tt http://baike.baidu.com/}}, both containing more than 6 million articles, are even larger than the English Wikipedia. If a knowledge base could be established between English Wikipedia and Chinese Hudong Baike, an English-Chinese knowledge base with much higher coverage in Chinese can be constructed.
\begin{figure}[h]
\centering
  \includegraphics[width=11cm]{fig_stat.png}\\
  \caption{Number of Articles on Major Wikipedias, Baidu Baike and Hudong Baike}
  \label{fig_stat}
\end{figure}

To enrich the Chinese knowledge, we try to build a large-scale English-Chinese knowledge base by semantifying four heterogeneous online wikis, which are English Wikipedia, Chinese Wikipedia, Hudong Baike and Baidu Baike. In this paper, we propose a unified framework to build such a knowledge base. The framework contains XXX steps: XXX, XXX, and XXXX. The generated knowledge base contains XXX classes, XXX instances and XXX properties. An online system supporting keyword search and SPARQL endpoint is also developed.

This non-trivial task poses the challenges as follows.
\begin{enumerate}
  \item The cross-lingual links are highly limited inside Wikipedia. For instance, there are only XXX English-Chinese links in Wikipedia. How could we find enough English-Chinese \verb"owl:sameAs" relations?
  \item The subsumption relations of the online wikis' category systems contain lots of noise. For example, in English Wikipedia ``Wikipedia-books-on-people", which is actually \verb"subClassOf" ``Books", is taken as the sub-category of ``People" mistakenly. How could we detect those incorrect semantic relations?
\end{enumerate}

Driven by these challenges, we propose a unified framework to build a English-Chinese knowledge base from four heterogeneous online wikis. Specifically, our work makes the following contributions.
\begin{enumerate}
  \item We extend the cross-lingual link set by employing a cross-lingual knowledge linking discovery approach for class and instance, and analyzing templates in Wikipedia for property.
  \item We prune the original taxonomy, which is extracted from encyclopedia category system, to retrieve more precise \textit{subClassOf} and \textit{instanceOf} relations in ontology.
  \item Both website and SPARQL endpoint are provided for public query operations over our knowledge base.
\end{enumerate}

The rest of the paper is organized as follows. Section \ref{sec:pd} presents some basic concepts and the problem formulation. In Section \ref{sec:dp} we presents we present our detailed approaches. The experimental results are reported in Section \ref{sec:result}. Some related work are described in Section \ref{sec:work}. Finally we conclude our work in Section \ref{sec:con}.

@@

\subsection{Web Access to Knowledge Base}
We provide a website to present an intuitive graph of our knowledge in the forms of class, instance and property. Fig.\ref{fig:xlore} shows sample pages of the integrated data. Users can choose language preference which is convenient for both English speaker and Chinese speaker. In the class webpage, we exhibit the label, super classes, subclasses, related topics, properties and instances of the specific class in bilingual way on condition that the corresponding English entries or Chinese entries exist.  In the instance webpage we display bilingual label, super classes, related classes, abstract, property key value pairs, images and references. In the property webpage, we present bilingual label, domains, ranges, and related instances of each property.
\begin{figure}[ht]
    \centerline{\includegraphics[width=1\columnwidth]{fig/xlore}}
    \caption{Sample Pages of Class, Instance and Property}
    \label{fig:xlore}
\end{figure}%
Beside these user-friendly pages, we provide two ways to access our knowledge base: via the search engine shown in Fig.\ref{fig:search-engine}, or via SPARQL endpoint shown in Fig.\ref{fig:sparql-endpoint}. For general users, they can make a query by inputing related text into searchbox and search to get entities with similar label. To present practicable result, An index is generated over all entities. We as well provide SPARQL interface for professional users to query our knowledge graph. Users can choose the language tags of their desired results by \textbf{"filter(langMatches(?label),"en"))"} or \textbf{"filter(langMatches (?label),"zh"))"}. For example, to get the English label of an instance, the query is: select * where {$<$\url{http://clkb/instance/100}$>$ $<$\url{http://www.w3.org/2000/01/rdf-schema#label}$>$ ?label. filter(langMatches(?label),"en"))}.

@@

\end{CJK*}
\end{document}
